---
title: "HUDM5124Assignment3"
author: "Zhuqian Zhou"
date: "2017/2/19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##PART B 
Kruskal’s Least-Squares Monotonic Transform

Here is the dissimilarity data for the digits data (note we could also start from the original (symmetrized) confusions for nonmetric MDS):
```{r}
n <- 5
DS <- matrix(c(0,875,800,125,890,875,0,600,850,670,800,600,0,925,675,125,850,925,0,890,890,670,675,890,0), nrow = n, byrow = FALSE, dimnames = list(c(1,2,3,4,5),c(1,2,3,4,5))) 
DS
```
Here are the coordinates for the 2-dimensional solution:
```{r}
C <- matrix(c(0.914, -0.660, -0.649, 0.923, -0.589, -0.229, -0.078, -0.648, 0.172, 0.716), nrow = n, byrow = FALSE, dimnames = list(c(1,2,3,4,5),c("d1","d2"))) 
C
```
1) Calculate the derived model distances between each pair of stimuli using the above coordinates (use the Euclidean distance metric).
```{r}
D <- matrix(rep(NA, 25), nrow = n, dimnames = list(c(1,2,3,4,5), c(1,2,3,4,5)))
for (i in 1:n) {
  for (j in 1:n) {
    D[i,j] = ((C[i,1]-C[j,1])^2+(C[i,2]-C[j,2])^2)^0.5 }}
D # a simpler way to do so is to use dist(C, method = "euclidean")
```
2) Re-order these model distances according to the order of the proximity data, and find the least-squares monotonic transform of the dissimilarities.
```{r, error=TRUE}
k <- 1
R <- as.vector(matrix(rep(NA, 10), nrow=1))
d <- as.vector(matrix(rep(NA, 10), nrow=1))
for (i in 2:n) {
  for (j in 1:(i-1)) {
    R[k] <- DS[i,j]
    d[k] <- D[i,j]
    k <- k+1
  }
}
R
d
R2 <- R
d2 <- d
m <- 10
for (j in 1:m) {
for (i in 1:(m-j)){
  if (R2[i] > R2[i+1]) {
    a <- R2[i]
    R2[i] <- R2[i+1]
    R2[i+1] <- a # bubble-sort the dissimilarity data, i.e. rank, R
    b <- d2[i]
    d2[i] <- d2[i+1]
    d2[i+1] <- b # re-order the distance data according to the rank
    }
  i = i+1}
j = j+1}
R2
d2
#D = (d(1,4)=0.40, d(2,3)=0.57, d(2,5)=0.80, d(3,5)=1.37, d(1,3)=1.62, d(2,4)=1.60, d(1,2)=1.58, d(1,5)=1.78, d(4,5)=1.61, d(3,4)=1.77)
#D = (0.40, 0.57, 0.80, 1.37, 1.62, 1.60, 1.58, 1.78, 1.61, 1.77)
#f (δ) = (0.40, 0.57, 0.80, 1.37, 1.61, 1.61, 1.58, 1.78, 1.61, 1.77)
#f (δ) = (0.40, 0.57, 0.80, 1.37, 1.60, 1.60, 1.60, 1.78, 1.61, 1.77)
#f (δ) = (0.40, 0.57, 0.80, 1.37, 1.60, 1.60, 1.60, 1.70, 1.70, 1.77)
```
3) Calculate stress 1 for this configuration.
```{r}
d3 <- c(0.40, 0.57, 0.80, 1.37, 1.62, 1.60, 1.58, 1.78, 1.61, 1.77)
f <- c(0.40, 0.57, 0.80, 1.37, 1.60, 1.60, 1.60, 1.70, 1.70, 1.77)
stress1 <- (sum((f-d3)^2)/(d3%*%d3))^0.5
stress1
```
